### 2017-03-08 Conclusion/Conclusion.tex
Final bits before submission

Searches for heavy neutral Higgs bosons decaying into pairs of tau leptons were performed
using $2.3\,\invfb$ of data recorded during the 2015
data-taking period of the \ac{LHC}, and using $12.9\,\invfb$ of 
data recorded during the first half of the 2016 data-taking period. The 
branching ratio of heavy neutral Higgs bosons into di-tau pairs is enhanced at high \tanb~in the \ac{MSSM},
making this one of the most sensitive search channels for such particles. Both analyses use a categorisation 
based on the presence of b-tagged jets to separate
the gluon fusion and b-associated production modes of Higgs bosons in the \ac{MSSM}. 
The hadronic tau isolation working point and the topological selection on 
the \mT~variable are chosen to optimise the search sensitivity for signal
masses of around $1\,\TeV$.
The sensitivity is maximised by using the \mTtot~variable for signal extraction.
This variable separates the dominant backgrounds
and the high-mass signal well.
No significant excess is observed in these searches, and so 
these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in \ac{MSSM} benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1 \cite{CMS-PAS-HIG-16-006,CMS-PAS-HIG-16-037}. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on $\PHiggsps/\PHiggs$ to date.

As more data are collected during the remainder of Run 2, and in the 
future, searches for \ac{MSSM} Higgs bosons in the di-tau final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
\ac{MSSM} benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to integrated luminosities of $300\,\invfb$ and $3000\,\invfb$ \cite{HTT-projection} is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
is very low in the high-\mA~and low-tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover this
parameter space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons, or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
at the 95\% CL of the 2015 MSSM analysis, projected to an integrated luminosity of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
 at the 95\% CL of the 2015 MSSM analysis (pink)
projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
under several assumptions of how the systematic uncertainties scale. Even with an integrated 
luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

>>>>

Searches for heavy neutral Higgs bosons decaying into pairs of tau leptons were performed
using $2.3\,\invfb$ of data recorded during the 2015
data-taking period of the \ac{LHC}, and using $12.9\,\invfb$ of 
data recorded during the first half of the 2016 data-taking period. The 
branching ratio of heavy neutral Higgs bosons into di-tau pairs is enhanced at high \tanb~in the \ac{MSSM},
making this one of the most sensitive search channels for such particles. Both analyses use a categorisation 
based on the presence of b-tagged jets to separate
the gluon fusion and b-associated Higgs boson production modes in the \ac{MSSM}. 
The hadronic tau isolation working point and the topological selection on 
the transverse mass between the electron or muon and the missing transverse energy are chosen to optimise the search sensitivity for signal
masses of around $1\,\TeV$.
The sensitivity is maximised by using the total transverse mass for signal extraction. This variable, which is 
the combination of the transverse
mass between the two legs of the di-tau candidate and the transverse masses between each of the legs
of the di-tau candidate and the missing transverse energy,
separates the dominant backgrounds
and the high-mass signal well.
No significant excess is observed in these searches, and so 
these analyses set limits on the production cross section times branching ratio of both the
gluon fusion and b-associated production processes. The results are also
interpreted in \ac{MSSM} benchmark scenarios, where the analyses exclude large areas
of the \mA-\tanb~plane, with significant improvement with respect to the most sensitive
results obtained in Run 1 \cite{CMS-PAS-HIG-16-006,CMS-PAS-HIG-16-037}. A combination of the 2015 and 2016 analyses is also
performed. This combination improves on the results of the 2016 analysis alone, thus
setting the most stringent limits on $\PHiggsps/\PHiggs$ production to date.

As more data are collected during the remainder of Run 2, and in the 
future, searches for \ac{MSSM} Higgs bosons in the di-tau final
state will continue. If no such Higgs bosons are found, these searches
will be able to exclude even more of the \mA-\tanb~plane in specific
\ac{MSSM} benchmark scenarios, although not all of the \mA-\tanb~plane
will become accessible. A projection of the results of the 2015 \ac{MSSM}
analysis to integrated luminosities of $300\,\invfb$ and $3000\,\invfb$ \cite{HTT-projection} is
shown in figure \ref{fig:mssm_projection_fig}. Even with an integrated luminosity of
$3000\,\invfb$ it is not possible to exclude the full \mA-\tanb~plane of this scenario,
as the branching ratio of $\PHiggsps/\PHiggs$ into di-tau pairs 
is very low in the high-\mA~and low-\tanb~corner. This region can be accessed 
via searches for the $\PHiggsps/\PHiggs \rightarrow \Ptop\APtop$ decay, which
has an enhanced branching ratio in this region. To fully cover this
parameter space it will therefore start to become more and more
important to combine searches for heavy Higgs bosons in different final states.
Doing this will give the best sensitivity to possible
heavy Higgs bosons, or in the absence of these particles exclusion
of the scenarios that predict them.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
at the 95\% CL of the 2015 MSSM analysis, projected to integrated luminosities of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
 at the 95\% CL of the 2015 MSSM analysis (pink)
projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
under several assumptions of how the systematic uncertainties scale. In scenario ``S1''
all systematic uncertainties are kept constant with integrated luminosity, while in scenario ``S2'' 
the theoretial uncertainties are scaled down by a factor $\frac{1}{2}$ and experimental
systematic uncertainties scale down by the square root of the integrated luminosity until they reach
a lower limit. In the ``Stat. Only'' scenario all systematic uncertainties are neglected. Even with an integrated 
luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario using this analysis alone \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

### 2017-03-08 Detector/Detector.tex
Final bits before submission

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%.
From all of the data that is recorded only a subset is used for analysis. Data is 
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the sub-systems it is made up of. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \acp{EE}
provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
Each endcap is divided into two halves. The preshower detectors, 
which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
The main use of the preshower detectors is to identifiy neutral pions decaying to two photons in the 
endcaps. Additionally,
they aid in the identification of electrons and improve the resolution
of the position determination. Each of the two preshower detectors consists
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower is three radiation lengths.

>>>>

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%.
Only a subset of the recorded data is used for analysis.
Data are
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the sub-systems it is made up of. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta$-$\phi$. The \acp{EE}
provide coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$.
Each endcap is divided into two halves. The preshower detectors, 
which are sampling calorimeters placed in front of the endcaps, cover a range of $1.653<|\eta|<2.6$.
The main use of the preshower detectors is to identify neutral pions decaying to two photons in the 
endcaps. Additionally,
they aid in the identification of electrons and improve the resolution
of the position determination. Each of the two preshower detectors consists
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower is three radiation lengths.
